Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-26 paper/main.tex
revision of supplementals mess v3

\todo[inline]{following list is exhaustive but probably too detailed}
%
Lastly, some contrasts of the audio-description stimulus yielded significant
clusters in regions that were not statistically significant in three or more
contrasts.
% details
In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% concludion statement
Here again, significantly increased activation beyond areas known to be involved
in processing of spatial information can be attributed to stimulus features of
the naturalistic stimulus that were not sufficiently controlled leading to a
bias in the contrasts.

@@

% intro
For each contrast we created several control contrasts.
% AV: no_cut > x
To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories (Tab.~\ref{tab:contrasts}).
%
None of these four contrasts yielded a significant cluster which suggest that
XYZ\todo{concluding statement}.

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
Given that cuts to a setting depicted for the first time (\texttt{vse\_new}) and
nouns indicating a a switch to a setting occurring for the first time
(\texttt{se\_new}), and cuts to a recurringly depicted setting
({\texttt{vse\_old}) and nouns indicating a switch a recurring setting
(\texttt{se\_old} turned out to be moderately correlated
(Fig.~\ref{fig:reg-corr}), we created a contrast that used the
audio-description's nouns on the movie data ({\texttt{se\_new} >
\texttt{se\_old}).
% results
The contrasts yielded a significant cluster in the right PPA and bilateral
clusters in the superior lateral occipital cortices (the right hemispheric
cluster extending into the superior parietal cortex).
%
Results suggest that XYZ.
\todo{concluding statement}

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
order to test XYZ.

\todo{why exactly did we do this except "we do not expect (lots of) significant
cluster because negative control?}
%
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.  \todo{explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.  \todo{concluding statement}.

>>>>

\todo[inline]{following list is exhaustive but probably too detailed}
%
Lastly, contrasts of the audio-description stimulus yielded significant clusters
in regions that were statistically in two or less contrasts.
% contrast 2
In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
% contrast 3
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
% contrast 6
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% contrast 7
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
% concluding statement
Here again, significantly increased activation beyond areas known to be involved
in processing of spatial information can be attributed to stimulus features of
the naturalistic stimulus that were not sufficiently controlled leading to a
bias in the contrasts.
%
\todo[inline]{imo other interpretations would speculative / reverse inference;
but "if would look closer I would probably find a super plausible reason why
brain areas are more active"}

@@

% intro
For each naturalistic stimus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories
(Tab.~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster.
%
Null results of control contrasts comparing frames within movie shots to frames
immediately after a cut suggest that XYZ.
%
\todo[inline]{concluding statement}

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
The inspection of correlations of regressors across stimuli
(Fig.~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
a setting occurring for the first time (\texttt{se\_new}), and cuts to a
recurringly depicted setting ({\texttt{vse\_old}) and nouns indicating a switch
a recurring setting (\texttt{se\_old}.
%
Hence, we created a contrast that used the audio-description's nouns on the
movie data ({\texttt{se\_new} > \texttt{se\_old}).
% results
The contrasts yielded a significant cluster in the right PPA and bilateral
clusters in the superior lateral occipital cortices (the right hemispheric
cluster extending into the superior parietal cortex).
%
Results suggest that XYZ.
%
\todo[inline]{concluding statement? That last contrast was originally done to
check that "soundscape at moment of cuts thing" but this is obsolete now}

\todo{following: control contrast for AO; why exactly did we do this except "we
do not expect (lots of) significant cluster because negative control?}

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
order to test XYZ.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.  \todo{explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.
%
\todo[inline]{concluding statement?}.
